---
title: "individual1"
output: html_document
---

# git init
#git add individual1.rmd invididual.html
#git commit 
#git status
#git remote add origin 

# Read data into dataframe.

# 1.) How are the ratings distributed? Draw a histogram of the ratings and describe it. Don’t forget to mention outliers, if there are any.

# A majority of the ratings fall between the value of 2 and 4 as seen by the high frequencies of the histogram.
# There seems to be an outlier that lies between 4.5 and 5. This is shown by the very small frequency. 


```{r}
choco <- read.csv("https://xdaiisu.github.io/ds202materials/hwlabs/choco.csv")
head(choco);
hist(choco$Rating, main = "Distribution of Ratings", xlab = "Ratings")
```


# 2.) Do ratings depend on the cacao percentage of a chocolate bar?

# By looking at the graph we can see that a higher cocoa % equates to a rating that has a range from 1 to 4 and it is almost evenly distributed. We can see from the graph that the highest rating is typically found at the 60-70% amount of cocoa.
```{r}
plot(choco$Cocoa.Pct,choco$Rating,main = "Rating vs. Cocoa %", xlab= "Cocoa %", ylab = "Rating")

```

